The Host Galaxies of 106 Rapidly Evolving Transients Discovered by the Dark Energy Survey

### 2020-08-13 DES_RET_Hosts_replyref2.tex
Updates from Overleaf

The host of \replyref{the rapidly evolving SN Ic-BL} SN2018gep appears more similar to the DES RET sample, lying in the same $M_*$-SFR and $M*$-sSFR plane, as well as lying below the MZR. While the SN2018gep \replyref{and CSS16100 hosts are} lower in stellar mass than any DES RET ($\log \left(M/M_{\odot}\right) =8.11$ \replyref{and $7.3$, respectively),} galaxies of that mass are unlikely to have been detected at the redshifts of the DES RETs \citep{Wiseman2020}. The authors' conclusion that SN2018gep is related to a shock-breakout of a massive, stripped-envelope star is similar to that posited in Section \ref{subsec:disc_origin}. \replyref{The host of the other SN Ic-BL we compare to, iPTF16asu, is slightly more massive, but otherwise consistent with SN2018gep.}

>>>>

The host of \replyref{the rapidly evolving SN Ic-BL} SN2018gep appears more similar to the DES RET sample, lying in the same $M_*$-SFR and $M*$-sSFR plane, as well as lying below the MZR. While the SN2018gep \replyref{and CSS16100 hosts are} lower in stellar mass than any DES RET ($\log \left(M/M_{\odot}\right) =8.11$ \replyref{and $7.3$, respectively),} galaxies of that mass are unlikely to have been detected at the redshifts of the DES RETs \citep{Wiseman2020}. The conclusion of \citet{Ho2019a} that SN2018gep is related to a shock-breakout of a massive, stripped-envelope star is similar to that posited in Section \ref{subsec:disc_origin}. \replyref{The host of the other SN Ic-BL we compare to, iPTF16asu, is slightly more massive, but otherwise consistent with SN2018gep.}
